Against the Planetary Interpretation of PTFO$\,$8-8695b

### 2020-04-16 paper/ms.tex
update paper

% \begin{figure*}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.9\textwidth]{f6.png}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{ {\bf Positions, kinematics, and HR diagram of \ptfo.}
%   Members of the 25$\,$Ori-1 subgroup are shown with black circles,
%   and were identified by \citet{kounkel_apogee2_2018} through
%   clustering on Gaia-DR2 and APOGEE data.  The ``neighborhood'' (gray
%   circles) is defined as the group of at most $10^4$ randomly selected
%   non-member stars within 5 standard deviations of the mean right
%   ascension, declination, and parallax.
% 	\label{fig:gaia}
% 	}
% \end{figure*}
\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf HR diagram of \ptfo\ and members of 25$\,$Ori-1.}
  Members of the 25$\,$Ori-1 group (black circles) were identified by
  \citet{kounkel_apogee2_2018} through clustering on six-dimensional
  Gaia-DR2 and APOGEE-2 data.  We defined the reference
  ``neighborhood'' (gray circles) as the group of at most $10^4$
  randomly selected non-member stars within 5 standard deviations of
  the mean 25$\,$Ori-1 right ascension, declination, and parallax.
  \ptfo\ seems likely to be a photometric binary.
	\label{fig:gaia}
	}
\end{figure*}

To assess the cluster membership, stellar mass, age, and potential
binarity of \ptfo, we need to identify stars with which it is and is
not coeval.  The simplest way to do this---clustering based on
six-dimensional position and kinematic information---has already been
done by \citet{kounkel_apogee2_2018}.  For simplicity, we considered
the members they identified brighter than $G_{\rm Rp}$ of 16.  This
yielded 149 members of 25$\,$Ori-1.

To define a set of non-associated stars with comparable selection
functions, we defined a reference ``neighborhood'' as the group of at
most $10^4$ randomly selected non-member stars within 5 standard
deviations of the mean 25$\,$Ori-1 right ascension, declination, and
parallax.  We queried these stars using the \texttt{astroquery}
package, which provides a convenient interface to the Gaia archive
(CITE, CITE).  This yielded 1{,}819 neighbor stars.  While some of
these stars may indeed be members of the Orion complex, or even of
25$\,$Ori-1, enforcing this cut on positions and parallaxes ensures
that we are querying stars with comparable amounts of interstellar
reddening.

We examined the resulting five-dimensional right ascension,
declination, proper motions, and parallaxes.  The first point we noted
was that 25$\,$Ori-1 was a clearly defined over-density in each
dimension---the cluster definitely exists, and is different from the
neighborhood.  \ptfo\ was also clearly a member in each of these
projected dimensions.

Given our detection of two separate signals, the issue of whether
\ptfo\ could be a photometric binary was of relatively high concern.
Figure~\ref{fig:gaia} shows the HR diagram from which we can assess
this question.

@@

\subsection{Short period dip}
The dip lasts about 45 minutes, and seems to re-occur every 11.74
hours
(Figures~\ref{fig:splitsignal},~\ref{fig:splitsignalii},~\ref{fig:phasefold}).
The dip duration is roughly the same as that observed by previous
investigators \citep{van_eyken_ptf_2012,yu_tests_2015,}
The dip depth is comparable to what has been observed in red visual
bands...
%TODO: and how does it compare to IR? bigger or smaller? cite relevant
%studies.

>>>>

% \begin{figure*}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.9\textwidth]{f6.png}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{ {\bf Positions, kinematics, and HR diagram of \ptfo.}
%   Members of the 25$\,$Ori-1 subgroup are shown with black circles,
%   and were identified by \citet{kounkel_apogee2_2018} through
%   clustering on Gaia-DR2 and APOGEE data.  The ``neighborhood'' (gray
%   circles) is defined as the group of at most $10^4$ randomly selected
%   non-member stars within 5 standard deviations of the mean right
%   ascension, declination, and parallax.
% 	\label{fig:gaia}
% 	}
% \end{figure*}
\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf HR diagram of \ptfo\ and members of 25$\,$Ori-1.}
  Members of the 25$\,$Ori-1 group (black circles) were identified by
  \citet{kounkel_apogee2_2018} through clustering on six-dimensional
  Gaia-DR2 and APOGEE-2 data.  We defined the reference
  ``neighborhood'' (gray circles) as the group of at most $10^4$
  randomly selected non-member stars within 5 standard deviations of
  the mean 25$\,$Ori-1 right ascension, declination, and parallax.
  \ptfo\ seems likely to be a photometric binary.
  ``$G$'' is the Gaia broadband, $Bp$ is Gaia blue, and $Rp$ is Gaia red.
  $\omega_{\rm as}$ is the parallax in arcseconds.
	\label{fig:gaia}
	}
\end{figure*}

To assess the cluster membership and potential
binarity of \ptfo, we needed to identify stars with which it was and was
not coeval.  The simplest way to do this---clustering based on
six-dimensional position and kinematic information---had already been
done by \citet{kounkel_apogee2_2018}.  For simplicity, we considered
the members they identified brighter than $G_{\rm Rp}$ of 16.  This
yielded 149 stars in 25$\,$Ori-1, mostly M dwarfs.
\citet{kounkel_apogee2_2018} identified seven other smaller
groups in the Orion complex near the Be star 25$\,$Ori. These groups
received higher numbers, {\it e.g.}, 25$\,$Ori-2.

To define a set of non-member stars that nonetheless had comparable selection
functions, we defined a reference ``neighborhood'' as the group of at
most $10^4$ randomly selected non-member stars within 5 standard
deviations of the mean 25$\,$Ori-1 right ascension, declination, and
parallax.  We queried these stars using the \texttt{astroquery}
package, which provides a convenient interface to the Gaia archive
(CITE, CITE).  This yielded 1{,}819 neighbors.  While some of
these stars may indeed be members of the Orion complex, or even of
25$\,$Ori-1, enforcing this cut on positions and parallaxes ensures
that we are querying stars with comparable amounts of interstellar
reddening.

We examined the resulting five-dimensional right ascension,
declination, proper motions, and parallaxes.  The first point we noted
was that 25$\,$Ori-1 was a clearly defined over-density in each
dimension, so the cluster exists, and is different from the
neighborhood.  \ptfo\ was also clearly a member in each of these
projected dimensions.

Given our detection of two separate signals, whether
\ptfo\ could be a photometric binary was of great interest.
Figure~\ref{fig:gaia} shows the HR diagram from which we assessed
this issue.
The diagram shows that \ptfo\ is $\approx$0.8 magnitudes brighter than the average
25$\,$Ori-1 star of the same color.
In other words, it is about twice as bright.
It also seems to be on the photometric binary track of the cluster, which has a few other stars.

The implication is that either 
{\it (i)} \ptfo\ is notably younger than the kinematically identical cluster members, or
{\it (ii)} \ptfo\ is a photometric binary.
Given the independent presence of two resolved signals,
we favor the interpretation that \ptfo\ is a binary star system.

@@

\subsection{Short period dip}
The dip lasts about 45 minutes, and seems to re-occur every 11.74
hours
(Figures~\ref{fig:splitsignal},~\ref{fig:splitsignalii},~\ref{fig:phasefold}).
The dip duration is roughly the same as that observed by previous
investigators \citep{van_eyken_ptf_2012,yu_tests_2015}
The dip depth is comparable to what has been observed in red visual
bands...
%TODO: and how does it compare to IR? bigger or smaller? cite relevant
%studies.
